---
title: "Dicamba Yield"
author: "Maxwel C. Oliveira"
date: "October 31, 2016"
output: word_document
---

```{r loadData, warning=FALSE, echo=FALSE, include=FALSE}
Dicamba=read.csv("Dicamba.csv")
str(Dicamba)
```

```{r loadPackage, warning=FALSE, echo=FALSE, include=FALSE}
library(drc)
```


```{r ConventionalLoadData, echo=FALSE, warning=FALSE, include=FALSE}
Conv<-Dicamba[(Dicamba$Soybean == 'Conventional'),]
```


##Conventional soybeans at 2nd trifoliate.
```{r Conventional 2nd, echo=FALSE, warning=FALSE}
Conv2=drm(YL~RateM, subset=Stage=="Second", fct=l3 (fixed =c(NA,50,NA)), data= Conv)
summary(Conv2)
modelFit(Conv2)

plot(Conv2, xlim=c(0,1000), xlab = expression(paste("Dicamba (g ae ha "^"-1",")")), ylab = expression(paste("Soybean Yield Loss (%)")))
```

```{r ED Conventional 2nd, echo=FALSE, warning=FALSE}
ED(Conv2, c(10,20,30,40,50))
```


##Conventional soybeans at R2.
```{r}
Conv<-Dicamba[(Dicamba$Soybean == 'Conventional'),]
ConvR=drm(YL~RateM, subset=Stage=="Rtwo", fct=l3 (fixed =c(NA,85,NA)), data=Conv) 
modelFit(ConvR) 
summary(ConvR) 

plot(ConvR, ylim=c(-10,100), xlim=c(0,100), xlab = expression(paste("Dicamba (g ae ha "^"-1",")")), ylab = expression(paste("Soybean Yield Loss (%)")))
```

```{r ED Conventional R2, echo=FALSE, warning=FALSE}
ED(ConvR, c(10,20,30,40,50,60,70,80,90))
```


```{r OrganicLoadData, echo=FALSE, warning=FALSE, include=FALSE}
Organic<-Dicamba[(Dicamba$Soybean == 'Organic'),]
str(Organic)
```

##Organic soybeans at 2nd trifoliate.
```{r Organic 2nd, echo=FALSE}
Org2=drm(YL~RateM, subset=Stage=="Second", fct=l3 (fixed =c(NA,55,NA)), data= Organic)
modelFit(Org2)
summary(Org2)
plot(Org2, xlim=c(0,1000), xlab = expression(paste("Dicamba (g ae ha "^"-1",")")), ylab = expression(paste("Soybean Yield Loss (%)")))
```

```{r ED Organic 2nd, echo=FALSE, warning=FALSE}
ED(Org2, c(10,20,30,40,50))
```

##Organic soybeans at R2.
```{r Organic R2, echo=FALSE}
OrgR=drm(YL~RateM, subset=Stage=="Rtwo", fct=l3 (fixed =c(NA,90,NA)), data= Organic)
modelFit(OrgR)
summary(OrgR)

plot(OrgR, ylim=c(-10,100), xlim=c(0,1000), xlab = expression(paste("Dicamba (g ae ha "^"-1",")")), ylab = expression(paste("Soybean Yield Loss (%)")))
```

```{r ED Organic R2, echo=FALSE, warning=FALSE}
ED(OrgR, c(10,20,30,40,50,60,70,80,90))
```


```{r GlyphosateLoadData, echo=FALSE, warning=FALSE, include=FALSE}
Glyphosate<-Dicamba[(Dicamba$Soybean == 'Glyphosate'),]
```

##Glyphosate soybeans at 2nd trifoliate.
```{r Glyphosate 2nd, echo=FALSE}
Gly2=drm(YL~RateM, subset=Stage=="Second", fct=l3 (fixed =c(NA,45,NA)), data= Glyphosate)
modelFit(Gly2)
summary(Gly2)
plot(Gly2, xlim=c(0,1000), xlab = expression(paste("Dicamba (g ae ha "^"-1",")")), ylab = expression(paste("Soybean Yield Loss (%)")))
```

```{r ED Glyphosate 2nd, echo=FALSE, warning=FALSE}
ED(Gly2, c(10,20,30,40,50))
```

##Glyphosate soybeans at R2.
```{r Glyphosate R2, echo=FALSE}
GlyR=drm(YL~RateM, subset=Stage=="Rtwo", fct=l3 (fixed =c(NA,85,NA)), data= Glyphosate)
modelFit(GlyR)
summary(GlyR)

plot(GlyR, xlim=c(0,1000), ylim=c(0,100), xlab = expression(paste("Dicamba (g ae ha "^"-1",")")), ylab = expression(paste("Soybean Yield Loss (%)")))
```

```{r ED Glyphosate R2, echo=FALSE, warning=FALSE}
ED(GlyR, c(10,20,30,40,50,60,70,80,90))
```


```{r GlufosinateLoadData, echo=FALSE, warning=FALSE, include=FALSE}
Glufosinate<-Dicamba[(Dicamba$Soybean == 'Glufosinate'),]
str(Glufosinate)
```

##Glufosinate soybeans at 2nd.
```{r Glufosinate 2nd, echo=FALSE}
Glu2=drm(YL~RateM, subset=Stage=="Second", fct=l3 (fixed =c(NA,50,NA)), data= Glufosinate)
modelFit(Glu2)
summary(Glu2)
plot(Glu2, xlim=c(0,1000), xlab = expression(paste("Dicamba (g ae ha "^"-1",")")), ylab = expression(paste("Soybean Yield Loss (%)")))
```

```{r ED Glufosinate 2nd, echo=FALSE, warning=FALSE}
ED(Glu2, c(10,20,30,40,50))
```


##Glufosinate soybeans at R2.
```{r Glufosinate R2, echo=FALSE}
GluR=drm(YL~RateM, subset=Stage=="Rtwo", fct=l3 (fixed =c(NA,100,NA)), data= Glufosinate)
modelFit(GluR)
summary(GluR)

plot(GluR, xlim=c(0,1000), xlab = expression(paste("Dicamba (g ae ha "^"-1",")")),
     ylab = expression(paste("Soybean Yield Loss (%)")))
```

```{r ED Glufosinate R2, echo=FALSE, warning=FALSE}
ED(GluR, c(10,20,30,40,50,60,70,80,90))
```


```{r LoadData at 2T, echo=FALSE, include=FALSE, warning=FALSE}
SecondT<-Dicamba[(Dicamba$Stage == 'Second'),]
str(SecondT)
```

###Plot at 2nd Trifoliate
```{r Models at 2T, echo=FALSE, warning=FALSE}
M2T=drm(YL~RateM, Soybean, fct=l3 (fixed =c(NA,55,NA)), data= SecondT)
modelFit(M2T)
summary(M2T)

plot(M2T, xlim=c(0,1000), legendPos = c(10,55), xlab = expression(paste("Dicamba (g ae ha "^"-1",")")), col=c(1,2,3,4), lty=c(1,2,3,4),lwd=2, pch=c(1,2,3,4), ylab = expression(paste("Soybean Yield Loss (%)")))
```

## ED's at 2nd Trifoliate
```{r ED at 2nd, echo=FALSE, warning=FALSE}
ED(M2T, c(10,20,30,40,50))
```

## Comparison of ED50 of drift at 2nd T
```{r EDcomp at 2T, echo=FALSE, warning=FALSE}
EDcomp(M2T, c(50,50))
```


```{r loadData at R2, echo=FALSE, include=FALSE, warning=FALSE}
R<-Dicamba[(Dicamba$Stage == 'Rtwo'),]
str(R)
```

###Plot at 2nd Trifoliate
```{r Models at Rtwo, echo=FALSE, warning=FALSE}
R2T=drm(YL~RateM, Soybean, fct=l3 (fixed =c(NA,100,NA)), data= R)
modelFit(R2T)
summary(R2T)

plot(R2T, xlim=c(0,1000), legendPos = c(10,55), xlab = expression(paste("Dicamba (g ae ha "^"-1",")")), col=c(1,2,3,4), lty=c(1,2,3,4),lwd=2, pch=c(1,2,3,4), ylab = expression(paste("Soybean Yield Loss (%)")))
```


## ED's at R2.
```{r ED at R2, echo=FALSE, warning=FALSE}
ED(R2T, c(10,20,30,40,50,60,70,80,90))
```

## Comparison of ED50 of drift at 2nd T.
```{r EDcomp at R2, echo=FALSE, warning=FALSE}
EDcomp(R2T, c(50,50))
```
